Experimental verification

### 2018-05-08 patent provisional/Experimental verification/Experimental verification.tex
updating the experimental verification section

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
%\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
%\newcommand{\hx}{\hat{x}} 
%\newcommand{\one}{\mathbf{1}} 
\newcommand{\SNR}{{\textsf{SNR}}}

@@

To be concrete, we formulate the problem for one-dimensional signals. The extension to multi-dimensional signals is straight-forward.

Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
The forward model can be posed as a mixture of {blind deconvolution} problems between binary signals and the target signals $x_i$:
\begin{equation} \label{eq:model}
y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
\end{equation}
The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$; see Figure~\ref{fig:micro_example} for an example. We assume that the nonzero values of $s$ are separated by at least $L-1$ entries. In the multi-dimensional case, this separation is imposed in each axis.

@@

\paragraph{Autocorrelation functions.}
We recall that the first-order autocorelation is the mean of the signals. For  
$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
\begin{align}
a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
Explicitly, the first three autocorrelations are
\begin{align} 
a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}

@@

Let $M_i$ denote the number of occurrences of the $i$th signal. 
Let us denote
\begin{align}
\gamma_k = \frac{M_k L}{N}.
\end{align}
Then, under the spacing constraint discussed above, one can show that
\begin{align} 
\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
\end{align}

\paragraph{Numerical experiments.}
In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$ . An example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
We used a micrograph of size $4000\times 4000$ and insert Einstein's images in random locations, while preserving the separation constraint. On average, each micrograph includes $860$ images. We then computed the first
We computed the first and second moment of the data and estimated the associated moments of the image using~\eqref{eq:data_ac}. We recall that the second moment is equivalent to the Fourier magnitude of the signal and therefore one can use standard phase retrieval algorithms. Here, we use an algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix} that iterates by 
\begin{equation}
x_{\ell+1} = x_\ell  + P_2(2P_1(x_\ell) - x_\ell) - P_1(x_\ell),
\end{equation}
where $P_2(z)$ combines the Fourier phases of $z$ with the Fourier magnitudes estimated from the data, and $P_1$ zeros out the signal out of its support. 
If the Fourier magnitude are estimated exactly, then the algorithm produces the signal or its reflection through the origin. 
In  we show an example how the reconstruction error decreases with as we collect more micrographs.

 \TODO{We have a movie in the supplementary material.} 
 \TODO{To add a figure of the error as a function of the number of micrographs.}

@@

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\RLL}{\mathbb{R}^{L\times L}}
%\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
%\newcommand{\hx}{\hat{x}} 
%\newcommand{\one}{\mathbf{1}} 
\newcommand{\SNR}{{\textsf{SNR}}}

@@

To be concrete, we formulate the problem for two-dimensional signals. 
Let $x_1,\ldots,x_K\in\RLL$ be the sought signals and let $y\in\RNN$ be the data (i.e., micrograph). 
The forward model can be posed as a mixture of {blind deconvolution} problems between binary signals and the target signals $x_i$:
\begin{equation} \label{eq:model}
y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I),
\end{equation}
where $\ast$ stands for convolution.
The nonzero values of each  $s_i\in\{0,1\}^{N\times N}$ determine the position of the occurrences of the corresponding $x_i$; see Figure~\ref{fig:micro_example} for an example for $K=1$. We assume a \emph{separation condition} on the binary signals $s=\sum_{i=1}^Ks_i$, that is, the nonzero values of $s$ are separated by at least $L-1$ entries in both axes.

@@

\paragraph{Autocorrelation functions.}
We recall that the first-order autocorelation is the mean of the signals. For  
$z\in\RL$ and $k\geq 2$, the autocorrelation of order $k$ is defined for any integer shifts $\ell_1, \ldots, \ell_{k-1}$ by
\begin{align}
a_z^k[\ell_1,\ldots,\ell_{k-1}]  & = \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}],
\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the bounds $0, \ldots, L-1$ is zero-padded, as usual.
Explicitly, the first three autocorrelations are
\begin{align} 
a_z^1 & = \sum_{i=0}^{L-1} z[i], \nonumber\\
a_z^2[\ell] & = \sum_{i = \max\{0, -\ell\}}^{L-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] & = \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{L-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}
The extension to multi-dimensional signals is straight-forward.

@@

Let $M_i$ denote the number of occurrences of the $i$th signal and  
let us denote
\begin{align}
\gamma_k = \frac{M_k L}{N}.
\end{align}
Then, under the spacing constraint discussed above, one can show that
\begin{align} 
\lim_{N\to\infty} a_y^1 & = \sum_{k=1}^K\gamma_k a_{x_k}^1, \nonumber\\
\lim_{N\to\infty} a_y^2[\ell] & = \sum_{k=1}^K\gamma_k a_{x_k}^2[\ell] +\sigma^2\delta[\ell],  \label{eq:data_ac}\\
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \sum_{k=1}^K\gamma_k a_{x_k}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{k=1}^K\gamma_k a_{x_k}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]). \nonumber
\end{align}
The same  holds for multi-dimensional signals.

\paragraph{Numerical experiments.}
In the first experiment, we estimated Einstein's image from micrographs contaminated with i.i.d.\ Gaussian noise with standard deviation of $\sigma=3$ . An example for such micrograph appears in the right panel of Figure~\ref{fig:micro_example}.

In the experiment, we generated $P$ micrographs, each of size $4000\times 4000$ pixels. 
Within each micrograph, Einstein's images were embedded in random locations, while preserving the separation constraint. On average, each micrograph contains $860$ images. We then computed the first
and second moment of the data and estimated the associated moments of the image using~\eqref{eq:data_ac}. We recall that the second moment is equivalent to the Fourier magnitude of the signal and therefore one can use standard phase retrieval algorithms to recover the signal, up to reflection through the origin. Here, we use an algorithm called relaxed-reflect-reflect (RRR)~\cite{elser2017matrix} that iterates by 
\begin{equation}
x_{\ell+1} = x_\ell  + P_2(2P_1(x_\ell) - x_\ell) - P_1(x_\ell),
\end{equation}
where $P_2(z)$ combines the Fourier phases of $z$ with the Fourier magnitudes estimated from the data, and $P_1$ zeros out the signal out of its support.

Figure~\ref{fig:Einst_example} shows three example for the reconstructed image using a different number of micrographs. Figure~\ref{fig:error_per_micro}  presents the normalized recovery error as a function of the number of micrographs used in the experiment. The error is computed by 
\begin{equation}
\text{recovery error} = \frac{\|x - \hat{x}\|\|x\|_{\text{F}}}{\|x\|_{\text{F}}},
\label{eq:error}
\end{equation}
where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$
denotes the Frobenius norm. We also present the normalized estimation error of the second-moment (power spectrum). The slope in a log-log plot is $-1/2$ as expected.

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}[h]{0.5\textwidth}
		\centering
	 \includegraphics[scale=0.6]{err_rrr_per_micrograph}
    \caption{\label{fig:error_per_micro}}	
	\end{subfigure}%
	\begin{subfigure}[h]{0.5\textwidth}
		\centering
	 \includegraphics[scale=0.6]{err_PS_per_micrograph}
\caption{}	
	\end{subfigure}%
	\caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined~\eqref{eq:error} in as a function of the number of the collected micrographs. The right panel presents the error of estimating the power spectrum of the signal from the data. As expected, in log-log scale, the curve has a $-1/2$ slope.}	
\end{figure}
